The Multi-Stencil Language

### 2016-05-27 ARTICLES/IJPP/article/article.tex
IJPP article modifications performance model
IJPP article modifications evaluation
IJPP article related work

\usepackage{todonotes}

@@

\author{Helene Coullon \and
        Christian Perez \and
        Julien Bigot
}

@@

%------------------------------------------------------------------------------
\section{Introduction}
\label{sect:introduction}
Contributions :
\begin{itemize}
\item Formalism of a multi-stencil program and its parallelization
\item The Multi-stencil Language: agnostic from the type of mesh and of the choosen implementation
\item A first implementation of the MSL compiler (static scheduling + fusion + dump to SkelGIS/components)
\item Evaluation of the different types of parallelism introduced + compiler + fusion
\end{itemize}
%------------------------------------------------------------------------------
\section{Computational model of Multi-Stencil Programs}
\label{sect:formalism}
\input{formalism.tex}
%------------------------------------------------------------------------------
\section{The Multi-Stencil Language}
\label{sect:msl}
\input{msl.tex}
%------------------------------------------------------------------------------
\section{Parallelization of Multi-Stencil Programs}
\label{sect:parallelism}
\input{parallelism.tex}
%------------------------------------------------------------------------------
\section{Static Scheduling and performance model}
\label{sect:msp}
\input{msp.tex}
%------------------------------------------------------------------------------
\section{Implementation}
\label{sect:comp}
\input{compiler.tex}
%------------------------------------------------------------------------------
\section{Evaluation}
\label{sect:eval}
\begin{itemize}
\item evaluation of the compiler (execution times of the different steps)
\item evaluation of the data parallelism (weak/strong scaling)
\item evaluation of fusions
\item evaluation of the hybrid performance
\item validation of the performance model
\end{itemize}

% \begin{figure}[!h]\begin{center}
%   \resizebox{8cm}{!}{\includegraphics{../results/weak_scaling/400/median_weak.pdf}}
%   \caption{weak-scaling 400x400 blocks.}
%   \label{fig:mesh}
% \end{center}\end{figure}

% \begin{figure}[!h]\begin{center}
%   \resizebox{8cm}{!}{\includegraphics{../results/weak_scaling/800/median_weak.pdf}}
%   \caption{weak-scaling 800x800 blocks}
%   \label{fig:mesh}
% \end{center}\end{figure}

% \begin{figure}[!h]\begin{center}
%   \resizebox{8cm}{!}{\includegraphics{../results/strong_scaling/10K_1K/median_strong.pdf}}
%   \caption{strong-scaling 10kx10k, 1k iterations}
%   \label{fig:mesh}
% \end{center}\end{figure}

% \item evaluation of the fusion

% \begin{figure}[!h]\begin{center}
%   \resizebox{8cm}{!}{\includegraphics{../results/task_scaling/500_200/fusVSbase.pdf}}
%   \caption{strong scaling 500x500, 200 iterations, with and without fusion}
%   \label{fig:mesh}
% \end{center}\end{figure}

% \item evaluation of the hybrid parallelism

% \begin{figure}[!h]\begin{center}
%   \resizebox{8cm}{!}{\includegraphics{../results/task_scaling/500_200/base_close_median.pdf}}
%   \caption{MPI only vs MPI+threads with \emph{close} scheduling policy (OpenMP)}
%   \label{fig:mesh}
% \end{center}\end{figure}

% \begin{figure}[!h]\begin{center}
%   \resizebox{8cm}{!}{\includegraphics{../results/task_scaling/500_200/base_spread_median.pdf}}
%   \caption{MPI only vs MPI+threads with \emph{spread} scheduling policy (OpenMP)}
%   \label{fig:mesh}
% \end{center}\end{figure}

% \item analytic model for the results

% \begin{figure}[!h]\begin{center}
%   \resizebox{8cm}{!}{\includegraphics{../results/task_scaling/500_200/analytic/times.pdf}}
%   \caption{Computation vs communication times in the MPI only application}
%   \label{fig:mesh}
% \end{center}\end{figure}

% \end{itemize}
%------------------------------------------------------------------------------
\section{Related work}
\label{sect:rel}
\begin{itemize}
\item stencil compilers cartesian : Pochoir, PATUS for optimizations/parallelization of a single stencil kernel
\item stencil compilers unstructured meshes : Lizst for optimizations/parallelization of a single stencil kernel
\item Halide and Nabla for pipeline of stencil computations in image (Cartesian) = mesh dependent
\item Reuse of external solutions as SkelGIS, GA, Lizst, Pochoir etc.
\end{itemize}
%------------------------------------------------------------------------------
\section{Conclusion}
\label{sect:concl}
%------------------------------------------------------------------------------

>>>>

\usepackage{todonotes}
\usepackage{url}
\usepackage{xspace}

\newcommand{\fix}[1]{\todo[inline,color=red!80]{#1}}
\newcommand{\cf}{\emph{cf.}\xspace}
\newcommand{\ie}{\emph{i.e.,}\xspace}
\newcommand{\llc}{L\textsuperscript{2}C\xspace}

@@

\author{Helene Coullon \and
        Julien Bigot \and
        Christian Perez
}

@@

%------------------------------------------------------------------------------
\section{Introduction}
\label{sect:introduction}
Contributions :
\begin{itemize}
\item Formalism of a multi-stencil program and its parallelization
\item The Multi-stencil Language: agnostic from the type of mesh and of the choosen implementation
\item A first implementation of the MSL compiler (static scheduling + fusion + dump to SkelGIS/components)
\item Evaluation of the different types of parallelism introduced + compiler + fusion
\end{itemize}
%------------------------------------------------------------------------------
\section{Related work}
\label{sect:rel}
\input{related.tex}
%------------------------------------------------------------------------------
\section{Computational model of Multi-Stencil Programs}
\label{sect:formalism}
\input{formalism.tex}
%------------------------------------------------------------------------------
\section{The Multi-Stencil Language}
\label{sect:msl}
\input{msl.tex}
%------------------------------------------------------------------------------
\section{Parallelization of Multi-Stencil Programs}
\label{sect:parallelism}
\input{parallelism.tex}
%------------------------------------------------------------------------------
\section{Static Scheduling and performance model}
\label{sect:msp}
\input{msp.tex}
%------------------------------------------------------------------------------
\section{Implementation}
\label{sect:comp}
\input{compiler.tex}
%------------------------------------------------------------------------------
\section{Evaluation}
\label{sect:eval}
\input{evaluation.tex}
%------------------------------------------------------------------------------
\section{Conclusion}
\label{sect:concl}
%------------------------------------------------------------------------------
